Singapore's Public Housing Affordability

### 2023-11-23 datastory.qmd
Project Update

For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230. While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.

@@

However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep. This suggests that the remaining lease period is not as strong an indicator as it was in 1990. Also, the data points are more spread out , inidcating a high variance in resale prices. We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.

@@

>>>>

For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD$5,230. While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.

@@

However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep. This suggests that the remaining lease period is not as strong an indicator as it was in 1990. Also, the data points are more spread out , indicating a high variance in resale prices. We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.

@@

<p style="text-align: justify; font-size: smaller;">
Bukit Timah Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/bukit-timah

DBS Singapore. (2023, October 10). What you need to know before getting a home loan | DBS Singapore. DBS. https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans.

CNA. (2023, October 2). HDB resale prices may keep rising moderately for rest of 2023: Analysts. CNA. https://www.channelnewsasia.com/singapore/hdb-resale-prices-q3-increase-moderate-supply-bto-2023-analysts-3813581

Household income - latest data. (n.d.-b). Base. https://www.singstat.gov.sg/find-data/search-by-theme/households/household-income/latest-data

Koh, J. (2023, November 19). Is the HDB Resale Flat Market Still Overheating? Seedly. https://blog.seedly.sg/hdb-resale-flats-price-high/

Kumar, S. (2022, April 11). Here’s The Salary You Need To Earn To Afford These Homes In Singapore [2022 Edition]. DollarsAndSense.sg. https://dollarsandsense.sg/salary-need-earn-afford-homes-singapore/

Liew, I. (2023, October 2). HDB resale prices up 1.2% in Q3, lower than quarter average in 2022; more flats sold. The Straits Times. https://www.straitstimes.com/singapore/housing/hdb-resale-prices-up-12-in-q3-lower-than-quarter-average-in-2022-more-flats-sold

Liew, I. (2023b, October 1). About 1,900 BTO flats in 2 Choa Chu Kang projects to be offered in early Oct launch. The Straits Times. https://www.straitstimes.com/singapore/housing/about-1900-bto-flats-in-2-choa-chu-kang-projects-to-be-offered-in-early-oct-launch

Lam, F. (2020, October 23). Singapore property agents urged to be ethical, give accurate advice. The Business Times. https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice

Lim, K. (2019, October 21). Property agent fined S$30,000, suspended 12 months over unethical bid to pocket bigger commission. TODAY. https://www.todayonline.com/singapore/property-agent-fined-s30000-suspended-12-months-over-unethical-bid-pocket-bigger

Tan, J. (2012, March 2). Online uproar over DPM Tharman’s ‘$1k flat’ statement. Yahoo Singapore. https://sg.news.yahoo.com/blogs/singaporescene/online-uproar-over-dpm-tharman-1k-flat-statement-132522414.html

Punggol Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/punggol

YCharts. (n.d.). 5-Year, 5-Year forward inflation expectation rate. https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate

<p>
